The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-05-17 paper/paper.tex
more in 4.6

A comparison of trained-edge and fixed-edge methods on the CosmoDC2 griz scenarios
is shown in Figure \ref{fig:edges}.  One important point to note is that while trained-edge
methods dominate the highest scores for the 3x2pt DETF metric, on which they trained, they
fare much worse on the lensing-only metrics (the methods were not re-trained on the lensing metrics;
we show the metrics for the same assigned bins).  This suggests that the difference between
optimal bins for different science cases is a significant one, and thus that analysis pipelines
should make it straightforward to calibrate multiple configurations and pass them to
subsequent science anlysis.

>>>>

A comparison of trained-edge and fixed-edge methods on the CosmoDC2 griz scenarios
is shown in Figure \ref{fig:edges}.  One important point to note is that while trained-edge
methods dominate the highest scores for the 3x2pt DETF metric, on which they trained, they
fare much worse on the lensing-only metrics (the methods were not re-trained on the lensing metrics;
we show the metrics for the same assigned bins).  This suggests that the difference between
optimal bins for different science cases is a significant one, and thus that analysis pipelines
should make it straightforward to calibrate multiple configurations and pass them to
subsequent science anlysis; this will probably be true even when comparing models with
different systematic parametrizations.  
This feature is highlighted by the comparison between the two variants
of the \textsc{NeuralNetwork} entry, which differed only in which metric they were targeting;
optimizing one metric does not optimize the other.
